StickleImputationCode

### 2025-09-04 R/StickleImputationCode.Rmd
updated imputations code.

```{r}
setwd('/Users/akhilghosh/Desktop/RStudioProjects2022Fall/SticklebackProject/RawData_ReadOnly')
stickle <- read_csv("AO.sexualdimorphismPruned.sc.forAnalysis_forMICE_Modeling_20June2023.csv")

@@

```

@@

combined_csv<- do.call(rbind,csv_list) %>% select(imp, time,gender, everything())
```

>>>>

```{r}
#setwd('/Users/akhilghosh/Desktop/RStudioProjects2022Fall/SticklebackProject/RawData_ReadOnly')
stickle <- read_csv("../RawData_ReadOnly/AO.sexualdimorphismPruned.sc.forAnalysis_forMICE_Modeling_20June2023.csv")

@@

#Manual Fixes
 # <!-- LQx.B.M.139 was called male in hand (and in our database) but is female by dissection. -->
 # <!-- LQx.B.M.155 was called male in hand (and in our database) but is female by dissection. -->
 # <!--     Pax.B.M.081 was called male in hand (and in our database) but is female by dissection. -->
 # <!--     Pax.L.M.113 was called male in hand (and in our database) but is female by dissection. -->
 # <!--     Pax.L.M.115 was called male in hand (and in our database) but is female by dissection. -->
stick$gender[stick$univID == "LQx.B.M.139"] <- "Female"
#stick$gender[stick$univID == "LQx.B.M.155"] <- "Female"
stick$gender[stick$univID == "Pax.B.M.081"] <- "Female"
stick$gender[stick$univID == "Pax.L.M.113"]<- "Female"
stick$gender[stick$univID == "Pax.L.M.115"] <- "Female"
```

@@

combined_csv<- do.call(rbind,csv_list) %>% select(imp, time,gender, everything())
write_csv(combined_csv, file = "../Data/updated_stickle_imputations_100_20250904.csv")
```
